Can we use masked priming in an online setting?

### 2021-05-06 Manuscript_intro_method_results_AB.Rmd
Update Manuscript_intro_method_results_AB.Rmd

\color{red}ADD at some point:

    - Hypotheses in a figure (as in Gomez & Perea, 2020).

\color{black}

@@

#### Rationale for sample size and stopping rule

@brysbaert2018 recommended that masked priming experiments should have at least 1,600 observations per condition. In order to account for potentially smaller effect sizes in an online experiment, we set a target of 3,000 observations per condition (12,000 observations total), which corresponds to a minimum of 50 participants given that there were 240 word stimuli in the experiment (see below). Our stopping rule was to keep collecting data until 3,000 valid observations were found. This goal was met and exceeded in our initial data collection with a budget of £200.

@@

We analyzed the data by fitting Bayesian linear and generalized linear mixed models, using the *brms* package [@R-brms_a; @R-brms_b] in R [@R-base][^1]. We only analyzed trials where the target stimulus was a word. For the response time (RT) analysis, we excluded trials with RTs lower than 250 ms and incorrect responses (`r exp1_data_to_include %>% filter(StimulusType == "Word") %>% {nrow(filter(., rt < 250 | rt > 2000 | corr == 0))/nrow(.)}*100` % of trials). For the accuracy analysis, we only excluded trials with RTs lower than 250 ms (`r exp1_data_to_include %>% filter(StimulusType == "Word") %>% {nrow(filter(., rt < 250 | rt > 2000))/nrow(.)}*100` % of trials). As the trials automatically ended after 2000 ms, there were no RTs longer than this. For both RTs and accuracy, we fitted a model with priming condition (unrelated vs. identical) and prime duration (33 ms vs. 50 ms) as well as their interaction as the fixed effects. For the discrete predictors, we used contrasts as follows: For priming condition, identical was coded as -1 and unrelated was coded as 1. For priming duration, 33 ms was coded as -1 and 50 ms was coded as 1. We used the maximal random effects structure possible, with random intercepts and slopes for condition, prime duration, and the interaction for participants and items. We used the ex-Gaussian distribution to model response times and the Bernoulli distribution (with a logit link) to model response accuracy. We used the default priors suggested by *brms* except for the coefficients for the fixed effects, for which we applied weakly informative priors of $\beta \sim N(0,100)$ in order to rule out improbably large effect sizes. Each model was fitted using four chains with 5000 iterations each (1000 warmup iterations). We consider an effect as credible if the 95% credible interval (CrI) estimated from the posterior distribution does not contain zero.

In addition, to better visualize the distributional features of the latency data, we computed the delta plots for both priming and prime duration effects.

@@

(ref:exp1-descriptives-rt-table-caption) Mean, median, standard deviation, and range of correct response times (in ms) and response accuracy (proportion of all responses) in Experiment 1 for words and nonwords and by prime duration and priming condition.

```{r exp1-descriptive-rt-table, as.is = TRUE,echo=FALSE}
#load raw Exp1 data

@@

apa_table(
  exp1_descriptives_rt
  , caption = "(ref:exp1-descriptives-rt-table-caption)"
  , note = "Trials with reaction times below 250 ms were excluded from the analysis. For the calculation of response times, incorrect responses were also removed."
  , escape = TRUE
)  
```

@@

```{r exp1-blmm-table, echo=FALSE, as.is = TRUE}
# We fit the models in a separate file to make sure that knitting the manuscript doesn't take too long

@@

(ref:exp1-brms-rt-plot-caption) 50%, 75%, 89%, 95%, and 100% highest density intervals (HDIs) of the posterior distributions for each of the parameters of the response time model in Experiment 1.

```{r exp1-brms-rt-plot, echo=FALSE, cache=TRUE, fig.cap = "(ref:exp1-brms-rt-plot-caption)"}

@@

plot(del_hdi_exp1_rt) +
  scale_fill_flat() + theme_apa()

#scale_fill_manual(values = c("dodgerblue4","dodgerblue3","dodgerblue2","deepskyblue1", "lightskyblue"), labels = c("50%", "75%", "85%", "95%", "100%"))+

@@

To better visualize the data, we computed the delta plots for the effect of Priming (see Panel A in Figure \@ref(fig:Deltas_E1_Words)), as well as for the effect of Prime Duration (see Panel B in Figure \@ref(fig:Deltas_E1_Words)). These delta plots are residual quantile plots that show the size of the effect for the .1, .3, .5, .7, and .9 response time quantiles.

(ref:Deltas_E1_Words-caption) Delta in Experiment 1...EXPLAIN.

```{r Deltas_E1_Words, echo=FALSE, cache=TRUE, fig.cap = "(ref:exp1-brms-rt-plot-caption)"}

@@

```{r exp1-acc-blmm-table, echo=FALSE, as.is = TRUE}

@@

#### Rationale for sample size and stopping rule

As in Experiment 1, our stopping rule was to keep collecting data until 3,000 valid observations were collected. This goal was met and exceeded in our initial data collection with a budget of £200.

@@

We analyzed the data in the same way as in Experiment 1, again only analyzing trials where the target stimulus was a word. For the response time (RT) analysis, we excluded trials with RTs lower than 250 ms and incorrect responses (`r exp2_data_to_include %>% filter(StimulusType == "Word") %>% {nrow(filter(., rt < 250 | rt > 2000 | corr == 0))/nrow(.)}*100` % of trials). For the accuracy analysis, we only excluded trials with RTs lower than 250 ms (`r exp2_data_to_include %>% filter(StimulusType == "Word") %>% {nrow(filter(., rt < 250 | rt > 2000))/nrow(.)}*100` % of trials). For priming duration, 16 ms was coded as -1 and 33 ms was coded as 1. Otherwise, the model specifications were identical to those in Experiment 1. W

@@

```{r exp2-descriptive-rt-table, as.is = TRUE,echo=FALSE}

@@

```{r load_exp2_brms_data, echo=FALSE, as.is = TRUE}
# We fit the models in a separate file to make sure that knitting the manuscript doesn't take too long
load("blmm_exp2_rt_dist_full_ranef_5000.RData")
# this file doesn't fit on GitHub
# download it at https://1drv.ms/u/s!ApE7JQmoH0baocIO3qh2TNb_TlqvlA?e=q3vJml
# model name is blmm_exp2_rt

@@

(ref:exp2-brms-rt-plot-caption) 50%, 75%, 89%, 95%, and 100% highest density intervals (HDIs) of the posterior distributions for each of the parameters of the response time model in Experiment 2.

```{r exp2-brms-rt-plot, echo=FALSE, cache=TRUE, fig.cap = "(ref:exp2-brms-rt-plot-caption)"}

#del_hdi_exp2_rt = hdi(blmm_exp2_rt_dist, ci = c(0.5, 0.75, 0.89, 0.95))
# brms (like any other lm-like function) automatically adds a "1" to the parameter name (for the contrast)
# get rid of the ones (and any other numbers) by using gsub 
#del_hdi_exp2_rt$Parameter <- del_hdi_exp2_rt$Parameter %>% gsub(pattern = "[[:digit:]]", replacement = "")
#plot(del_hdi_exp2_rt_dist) + scale_fill_flat() + theme_apa()
```

@@

```{r exp2_acc_brms_table, echo=FALSE, as.is = TRUE}

>>>>

\color{red} ADD: Hypotheses -> Model -> Data in a figure. \color{black}

@@

***Rationale for sample size and stopping rule.*** @brysbaert2018 recommended that masked priming experiments should have at least 1,600 observations per condition. In order to account for potentially smaller effect sizes in an online experiment, we set a target of 3,000 observations per condition (12,000 observations total), which corresponds to a minimum of 50 participants given that there were 240 word stimuli in the experiment (see below). Our stopping rule was to keep collecting data until 3,000 valid observations were found. This goal was met and exceeded in our initial data collection with a budget of £200.

@@

We analyzed the data by fitting Bayesian linear and generalized linear mixed models, using the *brms* package [@R-brms_a; @R-brms_b] in R [@R-base][^1]. We only analyzed trials where the target stimulus was a word. For the response time (RT) analysis, we excluded trials with RTs lower than 250 ms and incorrect responses (`r exp1_data_to_include %>% filter(StimulusType == "Word") %>% {nrow(filter(., rt < 250 | rt > 2000 | corr == 0))/nrow(.)}*100` % of trials). For the accuracy analysis, we only excluded trials with RTs lower than 250 ms (`r exp1_data_to_include %>% filter(StimulusType == "Word") %>% {nrow(filter(., rt < 250 | rt > 2000))/nrow(.)}*100` % of trials). As the trials automatically ended after 2000 ms, there were no RTs longer than this. For both RTs and accuracy, we fitted a model with priming condition (unrelated vs. identical) and prime duration (33 ms vs. 50 ms) as well as their interaction as the fixed effects. For the discrete predictors, we used contrasts as follows: For priming condition, identical was coded as -1 and unrelated was coded as 1. For priming duration, 33 ms was coded as -1 and 50 ms was coded as 1. We used the maximal random effects structure possible, with random intercepts and slopes for condition, prime duration, and the interaction for participants and items. We used the ex-Gaussian distribution to model response times and the Bernoulli distribution (with a logit link) to model response accuracy. We used the default priors suggested by *brms* except for the coefficients for the fixed effects, for which we applied weakly informative priors of $\beta \sim N(0,100)$ in order to rule out improbably large effect sizes. Each model was fitted using four chains with 5000 iterations each (1000 warmup iterations). We consider an effect as credible if the 95% credible interval (CrI) estimated from the posterior distribution does not contain zero.
In addition, to better visualize the distributional features of the latency data, we computed the delta plots for both priming and prime duration effects.

@@

(ref:exp1-descriptives-rt-table-caption) Mean, median, standard deviation, and range of correct response times (in ms) and response accuracy (proportion of all responses) in Experiment 1 for each condition.

```{r exp1-descriptive-rt-table, as.is = TRUE,echo=FALSE, warning=FALSE, message=FALSE}
#load raw Exp1 data

@@

apa_table(
  exp1_descriptives_rt
  , caption = "(ref:exp1-descriptives-rt-table-caption)"
  , escape = TRUE
)  
```

@@

```{r exp1-blmm-table, echo=FALSE, as.is = TRUE, warning=FALSE, message=FALSE}
# We fit the models in a separate file to make sure that knitting the manuscript doesn't take too long

@@

(ref:exp1-brms-rt-plot-caption) 50%, 75%, 89%, 95%, and 100% highest density intervals (HDIs) of the posterior distributions for each of the conditional parameters of the RT model in Experiment 1.

```{r exp1-brms-rt-plot, echo=FALSE, cache=TRUE, fig.cap = "(ref:exp1-brms-rt-plot-caption)", warning=FALSE, message=FALSE}

@@

del_hdi_exp1_rt%>%
  filter(!grepl("beta",Parameter)) -> posteriorsToPlot

plot(posteriorsToPlot) +
  scale_fill_flat(labels = c("50%", "75%", "89%", "95%", "100%")) +
  ylab("")+
  theme_apa() -> Plot_post_E1

Plot_post_E1

@@

To better visualize the data, we computed the delta plots for the effect of Priming (see Panel A in
Figure \@ref(fig:Deltas_E1_Words) ), as well as for the effect of Prime Duration (see Panel B in Figure \@ref(fig:Deltas_E1_Words) ). These delta plots are residual quantile plots that show the size of the effect for the .1, .3, .5, .7, and .9 response time quantiles.

```{r Deltas_E1_Words, echo=FALSE, cache=TRUE, fig.cap = "Delta in Experiment 1...EXPLAIN.", message=FALSE, warning=FALSE}

@@

```{r exp1-acc-blmm-table, echo=FALSE, as.is = TRUE, message=FALSE, warning=FALSE}

@@

***Rationale for sample size and stopping rule.*** As in Experiment 1, our stopping rule was to keep collecting data until 3,000 valid observations were collected. This goal was met and exceeded in our initial data collection with a budget of £200.

@@

We analyzed the data in the same way as in Experiment 1, again only analyzing trials where the target stimulus was a word. For the response time (RT) analysis, we excluded trials with RTs lower than 250 ms and incorrect responses (`r exp2_data_to_include %>% filter(StimulusType == "Word") %>% {nrow(filter(., rt < 250 | rt > 2000 | corr == 0))/nrow(.)}*100` % of trials). For the accuracy analysis, we only excluded trials with RTs lower than 250 ms (`r exp2_data_to_include %>% filter(StimulusType == "Word") %>% {nrow(filter(., rt < 250 | rt > 2000))/nrow(.)}*100` % of trials). For priming duration, 16 ms was coded as -1 and 33 ms was coded as 1. Otherwise, the model specifications were identical to those in Experiment 1. SAY SOMETHING ABOUT THE DELTAS

@@

```{r exp2-descriptive-rt-table, as.is = TRUE,echo=FALSE, message=FALSE, warning=FALSE}

@@

```{r load_exp2_brms_data, echo=FALSE, as.is = TRUE, message=FALSE, warning=FALSE}
# We fit the models in a separate file to make sure that knitting the manuscript doesn't take too long
load("blmm_exp2_rt_dist_full_ranef_5000.RData")
# this file doesn't fit on GitHub
# download it at https://1drv.ms/u/s!ApE7JQmoH0baocIO3qh2TNb_TlqvlA?e=q3vJml
# model name is blmm_exp2_rt

@@

(ref:exp2-brms-rt-plot-caption) 50%, 75%, 89%, 95%, and 100% highest density intervals (HDIs) of the posterior distributions for each of the conditional parameters of the RT model in Experiment 2.

```{r exp2-brms-rt-plot, echo=FALSE, cache=TRUE, fig.cap = "(ref:exp2-brms-rt-plot-caption)", message=FALSE, warning=FALSE}

del_hdi_exp2_rt = hdi(blmm_exp2_rt_dist, ci = c(0.5, 0.75, 0.89, 0.95))

del_hdi_exp2_rt%>%
  filter(!grepl("beta",Parameter)) -> posteriorsToPlotE2

plot(posteriorsToPlotE2) +
  scale_fill_flat(labels = c("50%", "75%", "89%", "95%", "100%")) +
  ylab("")+
  theme_apa() -> Plot_post_E2

Plot_post_E2

@@

```{r exp2_acc_brms_table, echo=FALSE, as.is = TRUE, message=FALSE, warning=FALSE}
